\documentclass[12pt]{article}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{geometry}
\geometry{margin=1in}

\title{Location HHI Augmentation Summary}
\date{\today}

\begin{document}
\maketitle

\section*{Overview}
We refreshed the firm-level location-concentration inputs to recover spells with missing MSAs. The update consisted of three high-level steps:
\begin{itemize}
  \item \textbf{User-level mapping.} \texttt{scripts/build\_user\_location\_lookup.py} normalises LinkedIn profile locations, strips county/township suffixes, handles foreign ``United States'' translations, splits hyphenated metro names, and merges in a priority alias list. The resulting lookup records a single best CBSA per \texttt{user\_id} with a match-quality tag.
  \item \textbf{Panel integration.} \texttt{scripts/build\_linkedin\_panel\_duckdb.py} and \texttt{scripts/build\_linkedin\_panel\_with\_remote.py} coalesce a spell's MSA-derived CBSA with the lookup fallback, keeping only one fallback CBSA per user and carrying a \texttt{cbsa\_from\_lookup} flag through the monthly and half-year panels.
  \item \textbf{Dual HHIs.} \texttt{scripts/build\_firm\_location\_hhi.py} now computes both the augmented measure (all spells) and the legacy baseline that excludes fallback rows, exposing \texttt{hhi}, \texttt{hhi\_original}, and their derivatives in \texttt{data/processed/firm\_location\_hhi.csv}.
\end{itemize}

\section*{Coverage Highlights}
The augmented panel captures substantially more dispersion:
\begin{itemize}
  \item Average \# CBSAs per firm--half-year increases from \num{20.0} (legacy) to \num{33.2}; the median rises from 5 to 6.
  \item The additional rows contribute roughly $48$ million headcount, bringing the total to about $79$ million (roughly \SI{61}{\percent} of headcount now originates from fallback CBSAs).
\end{itemize}

\section*{Startup Treatment Effects}
Table~\ref{tab:location_hhi_comparison} compares the startup interaction (var3/var5) under the augmented and legacy definitions. Numbers are coefficients with clustered standard errors in parentheses; \texttt{n} reports the regression sample size.
\begin{table}[ht]\centering
\caption{Startup Treatment Effects on Location HHI}
\label{tab:location_hhi_comparison}
\begin{tabular}{llcc}
\toprule
Param & Model & Augmented HHI & Legacy HHI \\
\midrule
var3 & OLS & $-0.058$ $(0.005)$\,$n=41{,}005$ & $-0.061$ $(0.005)$\,$n=40{,}593$ \\
var3 & IV  & $-0.110$ $(0.010)$\,$n=41{,}005$ & $-0.127$ $(0.011)$\,$n=40{,}593$ \\
var5 & OLS & $-0.001$ $(0.022)$\,$n=41{,}005$ & $-0.029$ $(0.023)$\,$n=40{,}593$ \\
var5 & IV  & $0.092$ $(0.088)$\,$n=41{,}005$ & $0.100$ $(0.092)$\,$n=40{,}593$ \\
\bottomrule
\end{tabular}
\end{table}
%
Table~\ref{tab:location_hhi_comparison} is generated by \texttt{writeup/py/create\_firm\_scaling\_location\_hhi\_table.py}, which reads \texttt{results/raw/firm\_scaling\_location\_hhi/consolidated\_results.csv}. The script has been updated to expose both ``all spells'' and ``legacy'' columns so the LaTeX table always reflects the latest regression output.

\begin{table}[ht]\centering
\caption{Startup Treatment Effects on Location HHI}
\label{tab:location_hhi_comparison}
\begin{tabular}{llcc}
\toprule
Param & Model & Augmented HHI & Legacy HHI \\\midrule
var3 & OLS & $-0.058$ $(0.005)$\, $n=41{,}005$ & $-0.061$ $(0.005)$\, $n=40{,}593$ \\
var3 & IV  & $-0.110$ $(0.010)$\, $n=41{,}005$ & $-0.127$ $(0.011)$\, $n=40{,}593$ \\
var5 & OLS & $-0.001$ $(0.022)$\, $n=41{,}005$ & $-0.029$ $(0.023)$\, $n=40{,}593$ \\
var5 & IV  & $\phantom{-}0.092$ $(0.088)$\, $n=41{,}005$ & $\phantom{-}0.100$ $(0.092)$\, $n=40{,}593$ \\
\bottomrule
\end{tabular}
\end{table}

\section*{Takeaways}
\begin{itemize}
  \item The new geography materially expands coverage (more CBSAs per firm and roughly $48$ million spells worth of headcount).
  \item The var3 startup effect remains negative and statistically significant under both definitions, with slightly smaller magnitude once fallback CBSAs are admitted.
  \item The var5 interaction stays statistically insignificant; point estimates shift closer to zero in the augmented measure and remain near zero in the legacy definition.
\end{itemize}

\end{document}
