\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{hyperref}

\sisetup{
  detect-mode,
  input-ignore = {,},
  table-format = +1.5,
  table-number-alignment = center
}

\title{Geography-Only Wage Component: Construction and Triple-Difference Results}
\author{}
\date{\today}

\begin{document}
\maketitle
\onehalfspacing

\section{Construction of the Geography Index}
\begin{enumerate}
    \item \textbf{Sample.} Use the precovid user panel and keep all observations with half-year identifier $yh < yh(2020,1)$ (the entire pre-COVID window).
    \item \textbf{Partial out firm, title, and time effects.} Estimate
    \[
        \log w_{it} = \alpha_{f(i)} + \theta_{k(i)} + \tau_{t} + u_{it}
    \]
    with \texttt{reghdfe} absorbing firm ($\alpha$), title ($\theta$), and half-year ($\tau$) fixed effects, and store the residuals $\hat{u}_{it}$.
    \item \textbf{Extract geography-only wages.} Run \texttt{reghdfe resid\_step1, absorb(w\_geo\_pre\_twostep=msa\_id)}; this stores the predicted geography component $\hat{\gamma}_{m}$ for each MSA.
    \item \textbf{Freeze and merge.} Use the estimated $\hat{\gamma}_{m}$ to assign a time-invariant geography-only log wage, $w^{\text{geo}}_{it} = \hat{\gamma}_{m(i)}$, consistent with the log wage scale, dropping MSAs without pre-period support.
\end{enumerate}

\section{Triple-Difference Specification}
Using the enriched panel, estimate the standard Remote~$\times$~Post~$\times$~Startup specification with $w^{\text{geo}}_{it}$ (the geography-only log wage) as the outcome.
Every regression absorbs user-by-firm and half-year fixed effects and clusters standard errors at the user level. The instrumental-variables specification instruments Remote~$\times$~Post and Remote~$\times$~Post~$\times$~Startup with the usual teleworkability shifters.

\section{Results}
\begin{table}[h!]
    \centering
    \caption{OLS Triple-Difference Estimates ($w^{\text{geo}}_{it}$)}
    \begin{tabular}{l S[table-format=+1.5]@{\,}l}
        \toprule
         & {Coef.} & {(s.e.)} \\
        \midrule
        Remote $\times$ Post & 0.00008 & (0.00012) \\
        Remote $\times$ Post $\times$ Startup & -0.00023 & (0.00019) \\
        Post $\times$ Startup & 0.00028 & (0.00016) \\
        \midrule
        Pre-period mean & \multicolumn{2}{c}{0.00002} \\
        Observations & \multicolumn{2}{c}{224{,}621} \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table}[h!]
    \centering
    \caption{IV Triple-Difference Estimates ($w^{\text{geo}}_{it}$)}
    \begin{tabular}{l S[table-format=+1.5]@{\,}l}
        \toprule
         & {Coef.} & {(s.e.)} \\
        \midrule
        Remote $\times$ Post & 0.00036 & (0.00103) \\
        Remote $\times$ Post $\times$ Startup & -0.00138 & (0.00121) \\
        Post $\times$ Startup & 0.00120 & (0.00086) \\
        \midrule
        Pre-period mean & \multicolumn{2}{c}{0.00002} \\
        Observations & \multicolumn{2}{c}{224{,}621} \\
        Kleibergen--Paap rk Wald $F$ & \multicolumn{2}{c}{122.99} \\
        \bottomrule
    \end{tabular}
\end{table}

\end{document}
