\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{amsmath,amssymb}
\usepackage{dsfont}
\usepackage[normalem]{ulem}
\usepackage{caption}
\captionsetup{labelformat=empty}

\newcommand{\cleanedresultsdir}{../results/cleaned/tex}

\begin{document}
\thispagestyle{empty}

\section*{Crunchbase Funding Outcomes Under the Firm Scaling Specification}

\paragraph{Setup.}
This note reports the baseline firm-scaling regression specification, replacing the original employment outcomes with Crunchbase-based funding outcomes.
The unit of observation is firm$\times$half-year, and the sample is restricted to firms that can be matched to Crunchbase.

\paragraph{Outcomes.}
We construct half-year outcomes from Crunchbase funding rounds:
\begin{itemize}
  \item \textbf{Any funding round}: indicator equal to 1 if the firm has at least one funding round announced in the half-year.
  \item \textbf{Log dollars raised}: $\log(1 + \text{USD raised})$, where USD raised is the total amount raised across rounds announced in the half-year.
\end{itemize}

\paragraph{Regression.}
We estimate the same OLS and IV specifications used in the firm-scaling analysis, using the same right-hand-side interactions and the same identification strategy (instrumenting remote adoption with pre-pandemic teleworkability).

\begin{table}[h!]
\caption{\textbf{Firm Scaling Spec with Crunchbase Funding Outcomes}}
\input{\cleanedresultsdir/firm_scaling_crunchbase_outcomes.tex}
\end{table}

\end{document}
