\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{amsmath,amssymb}
\usepackage{dsfont}
\usepackage[normalem]{ulem}
\usepackage{caption}
\usepackage{float}
\captionsetup{labelformat=empty}

\newcommand{\cleanedresultsdir}{../results/cleaned/tex}

\begin{document}
\thispagestyle{empty}

\section*{Crunchbase Fundraising: Actionable Follow-ups}

\paragraph{Scope.}
This note collects the meeting follow-ups that are actionable with the current repository artifacts:
sample maturity, VC fundraising recency, and re-estimated fundraising regressions under sample restrictions
(age cutoffs, intensive margin, ever-funded restriction) and geography splits (NY/SF vs.\ outside).
\par
\textbf{Not included: IPO truncation.} The transcript discussed excluding observations after IPO dates. We do not implement that here.

\paragraph{Sample.}
Unless stated otherwise, all results below use the matched, private Crunchbase analysis sample (firm$\times$half-year).

\begin{table}[H]
\caption{\textbf{Sample maturity: firm age cutoffs}}
\input{\cleanedresultsdir/firm_scaling_crunchbase_meeting_followups_maturity.tex}
\end{table}

\begin{table}[H]
\caption{\textbf{VC fundraising recency bins (as-of 2020-01-01)}}
\input{\cleanedresultsdir/firm_scaling_crunchbase_vc_recency.tex}
\end{table}

\paragraph{Fundraising follow-ups (log(1+USD raised)).}
We re-run the matched, private fundraising regressions under the requested restrictions. Models include firm fixed effects
and half-year fixed effects, with standard errors clustered at the firm level. We report both OLS and IV estimates of the
Remote$\times$Post coefficient (see \texttt{src/py/run\_crunchbase\_fundraising\_followups\_python.py}).

\begin{table}[H]
\caption{\textbf{Fundraising follow-ups: sample restrictions}}
\input{\cleanedresultsdir/firm_scaling_crunchbase_fundraising_followups_python_restrictions.tex}
\end{table}

\begin{table}[H]
\caption{\textbf{Fundraising follow-ups: geography splits and interaction}}
\input{\cleanedresultsdir/firm_scaling_crunchbase_fundraising_followups_python_geography.tex}
\end{table}

\end{document}
