\documentclass{article}
\usepackage[margin=1.15in]{geometry}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{float}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{dsfont}
\usepackage[normalem]{ulem}

\newcommand{\cleanedresultsdir}{../results/cleaned/tex}
\newcommand{\TableInput}[2][\linewidth]{\input{#2}}

\begin{document}

\section*{LLM Equity Heterogeneity: Observed-only Interaction + Split}

This note reports the default-spec heterogeneity design for the two core outcomes:
\texttt{firm\_scaling} and \texttt{user\_productivity\_precovid}. Both keep the core FE and IV setups and add:
(i) a pooled interaction model with equity-firm interactions, and
(ii) split baseline models for non-equity vs equity firms.
Unlike the baseline heterogeneity note, this version restricts to observations with
\texttt{llm\_n\_parse\_ok>0} before estimation.

\subsection*{Variables and construction}
\begin{itemize}
  \item \textbf{Core treatment terms (already in baseline specs).}
  \texttt{var3 = remote $\times$ covid}, \texttt{var5 = remote $\times$ covid $\times$ startup},
  \texttt{var4 = covid $\times$ startup}.
  For IV, \texttt{var6 = covid $\times$ teleworkable} and
  \texttt{var7 = startup $\times$ covid $\times$ teleworkable}.

  \item \textbf{LLM equity signal at firm$\times$half-year.}
  The merge panel (\texttt{latest\_firm\_yh\_llm\_equity.csv}) contributes
  \texttt{llm\_n\_parse\_ok} and \texttt{llm\_equity\_any}.
  In construction: \texttt{eq\_has\_parse = 1[llm\_n\_parse\_ok>0]},
  \texttt{eq\_any\_obs = llm\_equity\_any} only when parse is available,
  then \texttt{eq\_any\_firm = max(eq\_any\_obs)} within firm over time
  (missing set to 0), and \texttt{eq\_any\_firm\_covid = eq\_any\_firm $\times$ covid}.

  \item \textbf{Pooled interaction design.}
  Add interaction regressors
  \texttt{var3\_eq\_firm = var3 $\times$ eq\_any\_firm} and
  \texttt{var5\_eq\_firm = var5 $\times$ eq\_any\_firm}.
  IV instruments these with
  \texttt{var6\_eq\_firm = var6 $\times$ eq\_any\_firm} and
  \texttt{var7\_eq\_firm = var7 $\times$ eq\_any\_firm}.

  \item \textbf{Split design.}
  Re-estimate the baseline model separately in
  \texttt{eq\_any\_firm=0} and \texttt{eq\_any\_firm=1} subsamples using
  the same parameterization (\texttt{var3, var5, var4} with
  \texttt{var3,var5} instrumented by \texttt{var6,var7} in IV).

  \item \textbf{Outcomes kept from defaults.}
  Firm model reports \texttt{growth\_rate\_we}; user model reports
  \texttt{total\_contributions\_q100} in the \texttt{precovid} panel.
\end{itemize}

\subsection*{Table 1: Firm Scaling (interaction and split)}
\begin{table}[H]
  \centering
  \TableInput{\cleanedresultsdir/firm_scaling_llm_equity_heterogeneity_observed.tex}
\end{table}

\subsection*{Table 2: User Productivity (interaction and split)}
\begin{table}[H]
  \centering
  \TableInput{\cleanedresultsdir/user_productivity_llm_equity_heterogeneity_observed_precovid.tex}
\end{table}

\end{document}
